---
title       : Presetation on Iris prediction application
subtitle    : 
author      : Stuart Lyu
job         : Data Analyst
framework   : html5slides       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Idea behind the application

1. Predict iris species based on sepal length, sepal width, petal legth,petal width.
2. Based on the R default Iris dataset.
3. Utilize Randomforest for predictive modelling.

--- .class #id 

## Building model

1. break data set into training set and test set.
2. apply randomforest on the training set 

```{r, echo=TRUE,message=FALSE, warning=FALSE}
set.seed(1234)
ind <- sample(2, nrow(iris), replace=TRUE, prob=c(0.7, 0.3))
trainData <- iris[ind==1,]
testData <- iris[ind==2,]
library(randomForest)
rf <- randomForest(Species ~ ., data=trainData, ntree=100, proximity=TRUE)
``````

--- .class #id 

## model performance

we apply the model to the test dataset and see the performance is pretty good.

```{r, echo=FALSE,message=FALSE, warning=FALSE}
irisPred <- predict(rf, newdata=testData)
table(irisPred, testData$Species)
```

--- .class #id 

## link model to web input

we then link the web input to our built model to show the predicting result


```{r, echo=TRUE,message=FALSE, warning=FALSE}
library(shiny)
predictiris <- function(sepal_length, sepal_width, petal_length,petal_width,model=rf){
  data <- data.frame(sepal_length)
  data$"Sepal.Width" <- sepal_width
  data$"Petal.Length" <- petal_length
  data$"Petal.Width" <- petal_width
  names(data)[1] <-"Sepal.Length";
  irisPred <- predict(rf, data)
  return(as.character(irisPred))
}


shinyServer(
  function(input, output) {
    output$inputValue <- renderPrint({paste(input$sepal_length,input$sepal_width,input$petal_length,input$petal_width, sep=",")})
    output$prediction <- renderPrint({predictiris(input$sepal_length,input$sepal_width,input$petal_length,input$petal_width)})
  }
  )
```

--- .class #id 


## web front end

our web front end is very straight forward. Just inputs of 4 Iris attributes and a submit button


```{r, echo=TRUE,message=FALSE, warning=FALSE,cache=FALSE}
library(shiny)
shinyUI(
  pageWithSidebar(
    # Application title
    headerPanel("Iris prediction"),
    sidebarPanel(
      numericInput('sepal_length', 'Sepal Length', 1, min = 0.1, max =10 , step = 0.1),
      numericInput('sepal_width', 'Sepal Width', 1, min = 0.1, max =10 , step = 0.1),
      numericInput('petal_length', 'Petal Length', 1, min = 0.1, max =10 , step = 0.1),
      numericInput('petal_width', 'Petal Width', 1, min = 0.1, max =10 , step = 0.1),
      submitButton('Submit')
    ),
    mainPanel(
      h3('Results of prediction'),
      h4('You entered'),
      verbatimTextOutput("inputValue"),
      h4('Which resulted in a prediction of '),
      verbatimTextOutput("prediction"),
      h4('User Guide'),
      verbatimTextOutput("instruction")
    )
  )
)
```

